% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2009-2012 Derek R. Hildreth <derek@derekhildreth.com> http://www.derekhildreth.com 
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=black
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.95}
\definecolor{mygreylink}{gray}{.40}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.875in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubsubheading}[2]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textit{#1} & \textit{#2} \\
\end{tabular*}\vspace{-6pt}}
\renewcommand{\footnotesize}{\fontsize{10pt}{11pt}\selectfont}


\begin{document}

\newcommand{\mywebheader}{
	\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
		\textbf{{\LARGE Akshay Chiwhane}} \\
			\href{tel:248-278-1152}{Phone: 248-278-1152} |
			\href{mailto:achiwha@umich.edu}{Email: achiwha@umich.edu} |
			\href{https://github.com/achiwhane}{Github: achiwhane} |
			\href{https://linkedin.com/in/achiwhane}{Linkedin: /in/achiwhane}	\end{tabular*}
		\\
		\vspace{0.1in}}
		
		\mywebheader
		
		%%%%%%%%%%%%%%%%%%%%%%
		\resheading{Education}
		\begin{description}
			\item
			\ressubheading{{University of Michigan}}{Ann Arbor, MI}{B.S.E in Computer Science; GPA: 3.497/4.000}{Sept. 2014 -- April 2018 (Expected)}
			{ \footnotesize
				\begin{itemize}
					\resitem{\textbf{Key Courses:}
						Operating Systems (EECS 482), 
						Networks (EECS 489),
						Web Databases \& Information Systems (EECS 485),
						Intro to Machine Learning (EECS 445),
						Intro to Artificial Intelligence (EECS 492),
						Data Structures and Algorithms (EECS 281)
					}
					\resitem{\textbf{IEEE at the University of Michigan:}} 
					\begin{itemize}
						\resitem{Projects Chair - Gained exposure to frontend development by redesigning organization website using Jekyll and GitHub Pages}
						\resitem{Secretary - Helped plan, organize and communicate workshops and company-sponsored events for students} 
					\end{itemize}
					\resitem{\textbf{MHacks Core Team}} 
					\begin{itemize}
						\resitem{Backend Developer - Streamlined MHacks 8 registration process by developing REST API in Django to record QR code scans}
					\end{itemize}
				\end{itemize}
			}
		\end{description} % End Education list
		
		%%%%%%%%%%%%%%%%%%%%%%
		\resheading{Experience}
		\begin{description}
					\item 
			\ressubheading{DRW}{Chicago, IL}
			{Software Engineering Intern}{June 2017 - Aug. 2017}
			{	
				\footnotesize
				\begin{itemize}
					\resitem{Built data analysis frameworks and tools using Python, pandas, scipy, and slurm to assess and develop new trading strategies for options markets}
				\end{itemize}
			}
			\item 
			\ressubheading{Deepfield Networks}{Ann Arbor, MI}
			{Software Engineering Intern}{May 2016 -- Sept. 2016}
			{	
				\footnotesize
				\begin{itemize}
					\resitem{Improved speed and robustness of critical part of DDoS (Distributed Denial of Service) attack detection pipeline by architecting, developing, and optimizing DDoS analysis library using Python}
					\resitem{Gained familiarity with Agile and scrum (Atlassian Jira), test-driven development, and continuous integration methodologies (Jenkins)}
				\end{itemize}
			}
			\item 
			\ressubheading{Northrop Grumman}{Arlington, VA}
			{Extern}{May 2015 -- July 2015}
			{	
				\footnotesize
				\begin{itemize}
					\resitem{Simulated and evaluated packet scheduling schemes for content-centric networks using MATLAB}
					\resitem{Gained experience with project management and leadership skills through coursework}
				\end{itemize}
			}
			

			
		\end{description}  % End Experience list
		
		\resheading{Projects}
		
		\begin{description}
			\item[\href{https://github.com/achiwhane/Calculator}{Calculator:}] 
				{
					\footnotesize
					A reverse Polish Notation calculator with graphing capabilities for iOS, written in Swift.
				}
			\item[\href{https://github.com/achiwhane/ReadHN}{ReadHN:}] 
				{
					\footnotesize
					A Hacker News client for iOS, developed using Swift, Firebase, and AlamoFire.
				}
			\item[\href{https://github.com/achiwhane/playpong}{PongWithMe:}]
				{
					\footnotesize
					A game of pong where players use their phones to control paddles on a screen. Won 1st Place for the Best Use of Microsoft Platforms at MHacks IV.
				}
				
			\item[\href{https://github.com/achiwhane/ud851-Sunshine}{Sunshine:}]
				{
					\footnotesize
					A full-featured weather app for Android, completed as part of the ``Developing for Android''  Udacity course.
				}
			\item[\href{https://github.com/achiwhane/rrtracer}{RRTracer:}]
				{
					\footnotesize
					A ray tracer written in Rust.
				}
				
		\end{description}
		
		%%%%%%%%%%%%%%%%%%%%%%
		\resheading{Skills}
		\begin{description}
			\item[Programming Languages:]
				{	
					\footnotesize
					C++, C, Python, Rust, Java
				}
			\item[Frameworks/Technologies:]
				{
					\footnotesize
					Django, Tornado, Flask, Redis, Jupyter Notebooks, scikit-learn, pandas, numpy
				}
			\item[Languages:]
				{
					\footnotesize
					English (Fluent), Marathi (Fluent)
				}
		\end{description} % End Skills list
		
		
\end{document}